---
title: "lab7"
author: "Margaret Hammond"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs

Use GGally::ggpairs() function to create a pairs plot

```{r}
ggpairs(penguins)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, 
                            y = body_mass_g, 
                            group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")

```

## Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, 
                 data = penguins)

penguin_lm
```
How would you interpret this coefficient for flipper_length_mm?
On average, we expect a 1 mm increase in flipper length to be associated with a 51g (THIS SHOULD BE IN LINE CODE REFERENCE) increase in body mass. 

We would expect, on average, a 22.63 g increase in penguin body mass for each 1 mm increase in bill depth, if everything else is constant.

Use `summary()` function to get more info

```{r}
summary(penguin_lm)
```
The adjusted R-squared value in this: 75% of variance in penguin body mass is explained by this model. 24% of body mass that isn't explained. There is no good or bad R squared value. 

### Use `broom` functions tidy and glance

Use broom::tidy to get the coefficient summary in the data drame. 
Use broom::glance to get the model summary in a data frame.

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to (print) the bill depth coefficient

`r penguin_lm_tidy$estimate[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

### Try another model

We have thought really hard, done a literature review, consulted with experts, deeply explored our data and decided that the three most critical variables to include in this model (with body mass as the outcome variable) are: 
- flipper length
- species
- sex

Task: create a multiple linear regression model using those 3 predictor variables

Then take a look at the model outputs and interpret the coefficients with a neighbor

```{r}
penguin_lm_pt2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, 
                 data = penguins)

penguin_lm_pt2
```

Aedlie is the reference species, female is the reference sex. 
Mass(g) = -365.82 + 20.02(flipp(mm)) -87.63(Chinstrap) +836.26(gentoo) + 530.38(male)

If everything else is the same, we expect a Gentoo penguin to be 836 g heavier than an Adelie penguin. 

We had a female Chinstrap penguin with 180 mm flipper length. In our equation, it would be

-365.82+20.02(180)-87.63

Male adelie penguin with 200mm long flippers
-365.82+20.02(200)+530.38

### Use broom::augment() to see predicted values

```{r}
augment(penguin_lm_pt2)
```

## Use plot() to look at model diagnostics

```{r}

plot(penguin_lm_pt2)
```

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are reasonable predictor variables (make sure you're thinking hard about variables and different variable combinations)
- diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers (<< last one is not as assumption)

## Make output tables

Using modelsummary:
```{r}
modelsummary(penguin_lm_pt2)
```

Using stargazer:

```{r, results = "asis"}
stargazer(penguin_lm_pt2, type = "html")
```

