---
title: "lab7"
author: "Margaret Hammond"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
```

## Intro to ggpairs

Use GGally::ggpairs() function to create a pairs plot

```{r}
ggpairs(penguins)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, 
                            y = body_mass_g, 
                            group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")

```

## Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, 
                 data = penguins)

penguin_lm
```
How would you interpret this coefficient for flipper_length_mm?
On average, we expect a 1 mm increase in flipper length to be associated with a 51g (THIS SHOULD BE IN LINE CODE REFERENCE) increase in body mass. 

We would expect, on average, a 22.63 g increase in penguin body mass for each 1 mm increase in bill depth, if everything else is constant.

Use `summary()` function to get more info

```{r}
summary(penguin_lm)
```
The adjusted R-squared value in this: 75% of variance in penguin body mass is explained by this model. 24% of body mass that isn't explained. There is no good or bad R squared value. 

### Use `broom` functions tidy and glance

Use broom::tidy to get the coefficient summary in the data drame. 
Use broom::glance to get the model summary in a data frame.

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to (print) the bill depth coefficient

`r penguin_lm_tidy$estimate[3]`
